The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2024-06-07 Tables/transcribed.tex
edit for submission
prepare for restud submission

2     & \textbf{Mark with an "X" in the line below how likely is that you recover your pawn. } \\

@@

3     & \textbf{How much do you think the item you plan to pawn is worth?       \_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
4     & \textbf{Gender      } \\
5     & \textbf{Age} \\

@@

8     & \textbf{Education} \\

@@

9     & \textbf{In the last month, did a friend or family member asked you for money?} \\

@@

10    & \textbf{What would you like to have: 100 pesos tomorrow or 150 pesos in one month?} \\
11    & \textbf{How often do you feel stressed by your economic situation?} \\

@@

13    & \textbf{How stressed do you feel from the situation that led to to pawn?} \\

@@

14    & \textbf{In 3 months, I expect to have a  \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ situation} \\

@@

15    & \textbf{Have you panwned before?} \\

@@

16    & \textbf{How many times have you pawned on a Lender P branch?} \\

@@

17    & \multicolumn{1}{p{54.91em}}{\textbf{If you are saving money and a family member wants to use it for something }} \\

@@

18    & \textbf{Do you make an expenses budget for the month ahead of time?} \\

@@

20    & \textbf{Do you have savings?} \\

@@

21    & \textbf{Do you participate in a ROSCA?} \\

@@

22    & \textbf{Is it common that family or friends ask for money?} \\

@@

23    & \textbf{How much did you spend to come to the branch today?    \$\_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
24    & \textbf{How much time does it usually take to come to this branch?    \_\_\_\_\_\_\_\_\_\_\_} \\

@@

27    & \textbf{Does it happen to you that you spend more than you wanted because you fall into temptation?} \\

@@

28    & \textbf{In the last 6 months, has it happened that at some point you lacked money to pay} \\

@@

29    & \textbf{What would you like to have: 100 pesos in 3 months or 150 pesos in four months?} \\
30    & \textbf{Would you like to receive (free) reminders for upcomming payments?} \\

>>>>

\rowcolor[rgb]{ .682,  .667,  .667} 2     & \textbf{Mark with an "X" in the line below how likely is that you recover your pawn. } \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 3     & \textbf{How much do you think the item you plan to pawn is worth?       \_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
\rowcolor[rgb]{ .682,  .667,  .667} 4     & \textbf{Gender      } \\
\rowcolor[rgb]{ .682,  .667,  .667} 5     & \textbf{Age} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 8     & \textbf{Education} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 9     & \textbf{In the last month, did a friend or family member asked you for money?} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 10    & \textbf{What would you like to have: 100 pesos tomorrow or 150 pesos in one month?} \\
\rowcolor[rgb]{ .682,  .667,  .667} 11    & \textbf{How often do you feel stressed by your economic situation?} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 13    & \textbf{How stressed do you feel from the situation that led to pawn?} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 14    & \textbf{In 3 months, I expect to have a  \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ situation} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 15    & \textbf{Have you panwned before?} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 16    & \textbf{How many times have you pawned on a Lender P branch?} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 17    & \multicolumn{1}{p{54.91em}}{\textbf{If you are saving money and a family member wants to use it for something }} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 18    & \textbf{Do you make an expenses budget for the month ahead of time?} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 20    & \textbf{Do you have savings?} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 21    & \textbf{Do you participate in a ROSCA?} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 22    & \textbf{Is it common that family or friends ask for money?} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 23    & \textbf{How much did you spend to come to the branch today?    \$\_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
\rowcolor[rgb]{ .682,  .667,  .667} 24    & \textbf{How much time does it usually take to come to this branch?    \_\_\_\_\_\_\_\_\_\_\_} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 27    & \textbf{Does it happen to you that you spend more than you wanted because you fall into temptation?} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 28    & \textbf{In the last 6 months, has it happened that at some point you lacked money to pay} \\

@@

\rowcolor[rgb]{ .682,  .667,  .667} 29    & \textbf{What would you like to have: 100 pesos in 3 months or 150 pesos in four months?} \\
\rowcolor[rgb]{ .682,  .667,  .667} 30    & \textbf{Would you like to receive (free) reminders for upcomming payments?} \\
